% The Acknowledgements page, for thanking everyone
\clearpage
\pagestyle{plain}
\cfoot{\thepage}
\setstretch{2} % Reset the line-spacing to 1.3 for body text (if changed)
\acknowledgements{
    \addtocontents{toc}{\vspace{1em}} %Add a gap in the Contents, for aesthetic
    
    % The acknowledgements and the people to thank go here, don't forget to include your project advisor...
    
    % The following are examples of how to word your thanks
    
    First, I would like to express my sincere gratitude to my advisor Prof. Susan McRoy for the continuous support of my Ph.D study, for her patience, motivation, and immense knowledge. Her guidance helped me in my research and writing of this dissertation.
    
    I would also like to offer my special thanks to Dr Charles Welzig and the Welzig Neuroscience and Neurotechnology lab at the Medical College of Wisconsin. I benefited from the computational resource available in the lab to run the analyses and the computationally intensive simulations. My thanks also go to Zachary James Harper for his availability. Without his precious support it would have been impossible to conduct this research.
    
    My special thanks are extended to Dr Spencer (Chiang Ching) Huang of the Joseph Zilber School of Public Health. He has been crucial to the successful continuation of my PhD journey at the University of Wisconsin Milwaukee. The research assistantship he provided me has been a determining factor to my retention in the Doctoral program of Biomedical and Health Informatics.
    
    Finally, I would like to thank the rest of my dissertation committee: Prof Christine Cheng, Dr. Rohit Kate, and Dr. Zhang Qing, for their insightful comments, encouragement, and useful recommendations and suggestions which widen my research from various perspectives.
}
